\textcolor{black}{Disambiguating Monocular Depth Estimation with a Single Transient: Supplemental Information}

### 2020-07-11 paper/eccv2020CR/sections/discussion.tex
Updated While we acknowledge sentence
Paper down to 14 pages, ignore random log files.

The performance of our method is highly dependent on the accuracy of the initial
depth map of the MDE algorithm. Our results demonstrate that when the MDE
technique produces a depth map with good ordinal accuracy, where the ordering of
object depths is roughly correct, the depth estimate can be corrected to produce
accurate absolute depth. However, if the ordering of the initial depths is not
correct, these errors will not be corrected by our histogram matching procedure
and may propagate to the final output depth map.

In the optically diffused configuration, the laser
power is spread out over the entire scene. Accordingly, for distant scene points
very little light may return to the SPAD, \edit{ making reconstruction difficult (an analogous
  problem occurs with dark objects).} \edit{Thus, our method is best suited
  to short to medium-range scenes.}
\edit{CONSIDER MOVE THIS ENTIRE CALCULATION TO
SUPPLEMENT} For example, assuming an indoor scene with
fluorescent bulbs and an ambient spectral irradiance of $I_A =
1~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
to the laser), we find that the laser power required to achieve a minimum SBR of
5 for a diffuse scene at $R = 3$ m and a field of view of
$\theta = 40^\circ$\textdegree can be calculated as
%
\begin{equation}
  P_{\text{min}} = I_A \cdot 4 R^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
\end{equation}
giving $P_{\text{min}}=21$ mW. We note that this is significantly
less than the 60 mW used by the Kinect sensor to diffusely illuminate a scene.

Under these scene parameters, we can compute the total incident
flux on the detector per second (derived in~\cite{mcmanamon2012ladar}) as
\begin{equation}
  P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta
\end{equation}
where $P_T$ is the illumination power in the visible region, $\rho$ is its
albedo, $A_{rec}$ is the area of the detector region, $R$ is the distance to the
object, and $\eta$ is the quantum efficiency of the detector. For a range of
values similar to those of our experiments (detailed in the supplement), we find
that the ratio of photon detections to illumination pulses is roughly 4\%, or
well within low-flux regime where SPAD pileup is negligible~\cite{oconnortcspc}.
We also empirically validate that our method works with a diffused setup and
an output power of approximately 25 mW without significant pileup effects as
shown in Figure~\ref{fig:captured_diffuse_small} and detailed in the supplement.

\edit{We acknowledge that pileup in bright environments will ultimately limit
  the maximum range of our method. However, even when operating in the high-flux
  regime, pileup can be mitigated by reducing the amount of incident light, for
  example by reducing the aperture size or using neutral density filters, or by
  using pileup correction~\cite{Heide:2018,Rapp:2019}. Another approach to
  mitigate pileup involves taking two transient measurements, one with and one
  without laser illumination, and using their difference to approximate the
  backgrond-free transient.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Future Work}
\edit{DELETE While our hardware prototype is large, future work could miniaturize this
system.} Our algorithm or similar sensor fusion algorithms could
\edit{DELETE also} be integrated into electronics that already contain the required hardware
components, for example, existing cell phones with single-pixel SPAD
proximity sensors and RGB cameras \edit{The small baseline of such sensors
  would also mitigate the effects of shading and complex BRDFs. Necessary
  adjustments, such as pairing near-infrared (NIR) SPADs with NIR sensors,
  could be made. More sophisticated intrinsic imaging techniques could also be
  employed, replacing the primitive RGB channel method described here.}

Other methods for extracting scene information from a transient could be
employed, including learning-based methods to combine the MDE estimates and
histogram. One might even consider sensing regimes where the number of
returning signal photons is low, such as when the time-resolved detector and
camera operate at high framerates. While most MDE techniques are tailored to
clean RGB images, the transient could be used to help MDE techniques generalize
to noisy scenes under low-light conditions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Conclusions}
Since their introduction, monocular depth estimation algorithms have improved tremendously.  However, recent advances, which have generally relied on new network architectures or revised training procedures, have produced only modest performance improvements. 
In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with transient measurements. 
Such histograms are easy to capture using time-resolved single-photon detectors and are poised to become an important component of future low-cost imaging systems.
%Moving forward, sensor fusion is poised to become an even more important component of a variety of vision systems.
%Computational photography approaches may provide the measurements needed to achieve much greater performance improvements, especially as the sensors in devices we use every day become more diverse, complex, and increasingly rely on techniques based on sensor fusion and sophisticated computational algorithms.

>>>>

The performance of our method is highly dependent on the accuracy of the initial
depth map of the MDE algorithm. Our results demonstrate that when the MDE
technique produces a depth map with good ordinal accuracy, where the ordering of
object depths is roughly correct, the depth estimate can be corrected to produce
accurate absolute depth. However, if the ordering of the initial depths is not
correct, these errors may propagate to the final output depth map.

In the optically diffused configuration, the laser
power is spread out over the entire scene. Accordingly, for distant scene points
very little light may return to the SPAD, \edit{ making reconstruction difficult
(an analogous problem occurs with dark objects).} \edit{Thus, our method is
best suited to short- to medium-range scenes.}
\edit{On the other hand, in bright environments, pileup will ultimately limit the range of our
  method. However, this can be mitigated with optical elements to reduce the amount
  of incident light, with pileup correction~\cite{Heide:2018,Rapp:2019}, or
  even by taking two transient measurements, one with and one without laser
  illumination, and using their difference to approximate the background-free
  transient.}
\edit{Finally, under normal indoor conditions, it is theoretically possible to
  achieve an SBR of 5 at a range of 3 meters with a laser of only 21 mW while
  remaining in the low-flux regime. We confirm this empirically with our
  diffused setup, which operates without significant pileup effects while using
  approximately 25 mW of laser power (see
  Figure~\ref{fig:captured_diffuse_small} and the supplement for details).}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Future Work}
\edit{Future work could implement our algorithm or similar sensor fusion
  algorithms on smaller platforms such as existing cell phones with single-pixel SPAD
proximity sensors and RGB cameras. Necessary
  adjustments, such as pairing near-infrared (NIR) SPADs with NIR sensors,
  could be made. The small baseline of such sensors
  would also mitigate the effects of shading and complex BRDFs on the
  reflectance
  estimation step. More sophisticated intrinsic imaging techniques could also be
  employed.}

% \edit{DELETE Learning-based methods to combine the MDE estimates and
% histogram. One might even consider sensing regimes where the number of
% returning signal photons is low, such as when the time-resolved detector and
% camera operate at high framerates. While most MDE techniques are tailored to
% clean RGB images, the transient could be used to help MDE techniques generalize
% to noisy scenes under low-light conditions.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Conclusions}
Since their introduction, monocular depth estimation algorithms have improved
tremendously.  However, recent advances, which have generally relied on new
network architectures or revised training procedures, have produced only modest
performance improvements. In this work we dramatically improve the performance
of several monocular depth estimation algorithms by fusing their estimates with
transient measurements. Such histograms are easy to capture using time-resolved
single-photon detectors and are poised to become an important component of
future low-cost imaging systems.

%Moving forward, sensor fusion is poised to become an even more important component of a variety of vision systems.
%Computational photography approaches may provide the measurements needed to achieve much greater performance improvements, especially as the sensors in devices we use every day become more diverse, complex, and increasingly rely on techniques based on sensor fusion and sophisticated computational algorithms.

### 2020-07-11 paper/eccv2020CR/supplement.tex
Paper down to 14 pages, ignore random log files.

\section{Nominal values for radiometric calculation}
Here we give the values used in the equation for received power, repeated here
for convenience:
  \begin{equation}
    P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta.
  \end{equation}
  For our scene, we assume a vertical, planar, perfectly Lambertian surface. The following table gives the values used for this calculation.
\begin{figure}[H]
  \centering
  \begin{tabular}{c|c|c}
    \toprule
    Symbol & Description & Nominal Value \\
    \midrule
    $\rho$  & Albedo of lambertian surface & $0.3$ \\
    $P_T$ & Total irradiance at wavelength (W/$\text{m}^2$) & $0.026$ \\
    $R$ & Distance to surface (m) & $3$ \\
    $A_{rec}$ & Area of detector ($\text{m}^2$) & $1.96 \times 10^{-9}$ \\
    $\eta$ & Quantum efficiency of detector & $0.3$ \\
    $P_R$ & Received power at detector (W) & $1.62 \times 10^{-13}$ \\
    \bottomrule
  \end{tabular}
  \caption{Table of nominal values for radiometric calculation.}
  \label{fig:sbr_calculation}
\end{figure}
Once $P_R$ is determined, we compute the number of photons using the laser
wavelength $\lambda = 532$ nm as
\begin{equation}
  N = \frac{P_R\lambda}{hc}
\end{equation}
where $h \approx 6.626 \times 10^{-34}$ $\text{J} \cdot \text{s}$ is Planck's constant and $c \approx 3
\times 10^8$ $\text{m}/\text{s}$ is the speed of light. Using the fact that our laser runs at 10
MHz, we get the number of photons per pulse as $0.043$ or $4.3\%$, which puts us in the
low-flux regime (where photons per pulse is $< 5\%$).

>>>>

\section{Radiometric calculation}
Assuming an indoor scene with fluorescent bulbs and an ambient spectral irradiance of $I_A =
1~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
to the laser), we find that the laser power required to achieve a minimum SBR of
5 for a diffuse scene at $R = 3$ m and a field of view of
$\theta = 40^\circ$\textdegree can be calculated as
%
\begin{equation}
  P_{\text{min}} = I_A \cdot 4 R^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
\end{equation}
giving $P_{\text{min}}=21$ mW. We note that this is significantly
less than the 60 mW used by the Kinect sensor to diffusely illuminate a scene.

Under these scene parameters, we can compute the total incident
flux on the detector per second (derived in~\cite{mcmanamon2012ladar}) as
\begin{equation}
  P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta
\end{equation}
where $P_T$ is the illumination power in the visible region, $\rho$ is its
albedo, $A_{rec}$ is the area of the detector region, $R$ is the distance to the
object, and $\eta$ is the quantum efficiency of the detector.
% For a range of
% values similar to those of our experiments, we find
% that the ratio of photon detections to illumination pulses is roughly 4\%, or
% well within low-flux regime where SPAD pileup is negligible~\cite{oconnortcspc}.

For scene itself, we assume a vertical, planar, perfectly Lambertian surface. The following table gives the values used for this calculation.
\begin{figure}[H]
  \centering
  \begin{tabular}{c|c|c}
    \toprule
    Symbol & Description & Nominal Value \\
    \midrule
    $\rho$  & Albedo of lambertian surface & $0.3$ \\
    $P_T$ & Total irradiance at wavelength (W/$\text{m}^2$) & $0.026$ \\
    $R$ & Distance to surface (m) & $3$ \\
    $A_{rec}$ & Area of detector ($\text{m}^2$) & $1.96 \times 10^{-9}$ \\
    $\eta$ & Quantum efficiency of detector & $0.3$ \\
    $P_R$ & Received power at detector (W) & $1.62 \times 10^{-13}$ \\
    \bottomrule
  \end{tabular}
  \caption{Table of nominal values for radiometric calculation.}
  \label{fig:sbr_calculation}
\end{figure}
Once $P_R$ is determined, we compute the number of photons using the laser
wavelength $\lambda = 532$ nm as
\begin{equation}
  N = \frac{P_R\lambda}{hc}
\end{equation}
where $h \approx 6.626 \times 10^{-34}$ $\text{J} \cdot \text{s}$ is Planck's constant and $c \approx 3
\times 10^8$ $\text{m}/\text{s}$ is the speed of light. Using the fact that our laser runs at 10
MHz, we get the number of photons per pulse as $0.043$ or $4.3\%$, which puts us in the
low-flux regime (where photons per pulse is $< 5\%$)~\cite{oconnortcspc}.
